D3064R0: OOTA Execution on Real Implementations is Provably Vacuous

### 2024-01-04 ootavacuous.tex
Add OOTA-definition examples for context and loads
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

@@

@@

\emph{A C++ implementation must assume that a given dependency is
a semantic dependency unless and until it can prove otherwise.}

>>>>

A similar caution applies to loads:

\begin{quote}
	\co{r1 = x;} \\
	\co{if (r1 > 42)} \\
	\co{\ \ \ \ r2 = y;} \\
	\co{else} \\
	\co{\ \ \ \ r2 = y;} \\
	\co{z = r2;}
\end{quote}

The two loads from \co{y} are fungible, and one should therefore expect
a compiler to replace this \co{if} statement with a single load from \co{y}.

@@

\subsubsection{Semantic Dependencies Depend on Context}
\label{sec:Semantic Dependencies Depend on Context}

Consider the following:

\begin{quote}
	\co{r1 = x;} \\
	\co{// r1 = 0;} \\
	\co{z = y * r1;} \\
	\co{// z = y / r1;}
\end{quote}

As written, there is a semantic dependency from \co{x} and \co{y}
to \co{z}.
But if the second line is uncommented, there is no semantic
dependency.
If the second line is left commented, but the last line is uncommented,
then the compiler is free to backwards-propagate the potential
divide-by-zero undefined behavior to precede the first assignment
to \co{z}.
This could prevent both assignments to \co{z} from executing, for example,
due to a divide-by-zero exception.

More subtle changes in context can also have an effect.
For example:

\begin{quote}
	\co{r1 = x;} \\
	\co{z = y * r1;} \\
	\co{z = 42;}
\end{quote}

Given that there is no ordering, a C++ implementation could choose to
act as if the first store to \co{z} was omitted, even if that store was
a relaxed atomic store.
But if \co{z} was marked volatile, both stores would need to be executed
in strict accordance with the rules of the abstract machine.

\emph{Any analysis of semantic dependencies must either be fully informed
of the enclosing context, or much make conservative assumptions about
that context.}

@@

\emph{Because of unsolved mathematical problems, precise definitions of
``semantic dependency'' are problematic.
Therefore, C++ implementations must assume that a given dependency is
a semantic dependency unless and until it can prove otherwise.}
